The Second Data Release of the INT Photometric H$\alpha$ Survey of the Northern Galactic Plane (IPHAS DR2)

### 2014-03-12 paper/iphas-dr2.tex
Now (45,2)

In contrast, closer towards the galactic
centre at $l=45^\circ$ (Fig.~\ref{fig:l45})
we find a wealth of reddened objects
which appear to be separated into a lowly
and a highly reddened component,
perhaps revealing two distinct parts of the Galaxy.

>>>>

In contrast, 
closer towards the galactic centre at $l=45^\circ$ (Fig.~\ref{fig:l45}) we find a wealth of reddened objects.
In the colour magnitude diagram it is clear that the stars are split into two distinct groups,
with one significantly redder than the other.
The bluer group is composed of main sequence stars,
with the slope of this group in the colour magnitude diagram attributable to the significantly increasing extinction.
Meanwhile the redder group is principally composed of red giant stars.
As these stars are intrinsicly brighter,
at some given apparent magnitude they will be substantially further away than their main sequence counterparts.
Given that, along this sightline,
extinction continues to increase with distance,
the red giants we observe will be subject to more reddening than a main sequence star exhibiting the same apparent magnitude.
Therefore, the clear split between the two groups arises due to the combination of increasing extinction and the distinct absolute magnitude ranges of main sequnce and giant branch stars.
